Title

### 2020-10-11 latex-article/article.tex
Added Notes in Table as an example
Updated slide colors

\begin{table}[tp] \centering 
\caption{Summary Statistics}
\label{summ_stat}
    \begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
    \hline 
    \hline \\[-1.8ex] 
    Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\ 
    \hline \\[-1.8ex] 
    rating & 30 & 64.633 & 12.173 & 40 & 58.8 & 71.8 & 85 \\ 
    complaints & 30 & 66.600 & 13.315 & 37 & 58.5 & 77 & 90 \\ 
    privileges & 30 & 53.133 & 12.235 & 30 & 45 & 62.5 & 83 \\ 
    learning & 30 & 56.367 & 11.737 & 34 & 47 & 66.8 & 75 \\ 
    raises & 30 & 64.633 & 10.397 & 43 & 58.2 & 71 & 88 \\ 
    critical & 30 & 74.767 & 9.895 & 49 & 69.2 & 80 & 92 \\ 
    advance & 30 & 42.933 & 10.289 & 25 & 35 & 47.8 & 72 \\ 
    \hline \\[-1.8ex] 
    \end{tabular}

@@

\begin{table}[tb] \centering 
    \caption{Regression Results} 
    \label{reg1}

>>>>

\begin{table}
    \caption{Column Width Resize Box Table}
    \centering

    \begin{center}
    \resizebox{\columnwidth}{!}{
        \begin{tabular}{@{\extracolsep{5pt}}lcccccccc}
            \hline 
            & & & \multicolumn{2}{c}{Market Access} & \multicolumn{2}{c}{Urban Weekly Wage} & \multicolumn{2}{c}{Nonurban Weekly Wage} \\
            \cline{4-5} \cline{6-7} \cline{8-9}
            Year & N & \% Urban & Mean & SD & Mean & SD & Mean & SD \\ \hline

            % \input{summary.tex}

            1940 & 16,875,829 & 0.66 & 10,708.21 & 14,819.55 & 33.22 & 19.66 & 25.23 & 16.56\\
            1950 & 67,790 & 0.69 & 23,166.06 & 26,600.85 & 70.05 & 32.70 & 58.27 & 29.24\\
            1960 & 1,338,491 & 0.66 & 40,328.17 & 45,385.47 & 124.11 & 77.55 & 99.37 & 59.01\\
            1970 & 277,951 & 0.75 & 65,373.07 & 68,048.88 & 205.42 & 137.80 & 165.61 & 104.49\\
            1980 & 1,907,836 & 0.73 & 73,223.43 & 74,906.62 & 408.83 & 284.44 & 340.82 & 220.68\\
            1990 & 2,257,874 & 0.68 & 224,312.50 & 168,933.04 & 711.77 & 574.58 & 550.26 & 392.90\\
            2000 & 2,581,741 & 0.73 & 288,195.77 & 199,100.92 & 1,010.36 & 1,022.77 & 754.10 & 649.57\\
            2005 & 530,283 & 0.76 & 283,709.53 & 196,293.00 & 1,211.38 & 1,203.62 & 881.47 & 722.94\\
            2010 & 530,359 & 0.76 & 273,754.31 & 195,220.04 & 1,306.70 & 1,281.34 & 972.40 & 817.94\\
            2015 & 559,168 & 0.76 & 252,832.47 & 164,905.15 & 1,447.26 & 1,545.33 & 1,080.38 & 1,011.25\\

            \hline

            \multicolumn{9}{p{.8\textwidth}}{\textit{Notes.} Weekly wage is reported in 2015 \$.}
        \end{tabular}
    }
    \end{center}
\end{table}

\begin{table}[tp] 
    \caption{Summary Statistics}
    \label{summ_stat}
    \centering

    \begin{tabular}{lccccccc} 
        \hline 
        \hline \\[-1.8ex] 
        Statistic & N & Mean & St. Dev. & Min & Pctl(25) & Pctl(75) & Max\\ 
        \hline \\[-1.8ex] 
        rating & 30 & 64.633 & 12.173 & 40 & 58.8 & 71.8 & 85 \\ 
        complaints & 30 & 66.600 & 13.315 & 37 & 58.5 & 77 & 90 \\ 
        privileges & 30 & 53.133 & 12.235 & 30 & 45 & 62.5 & 83 \\ 
        learning & 30 & 56.367 & 11.737 & 34 & 47 & 66.8 & 75 \\ 
        raises & 30 & 64.633 & 10.397 & 43 & 58.2 & 71 & 88 \\ 
        critical & 30 & 74.767 & 9.895 & 49 & 69.2 & 80 & 92 \\ 
        advance & 30 & 42.933 & 10.289 & 25 & 35 & 47.8 & 72 \\ 
        \hline \\[-1.8ex] 
    \end{tabular}

@@

\begin{table}[tb] 
    \caption{Regression Results} 
    \label{reg1}
    \centering
